Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-11 paper/disc20clustering.tex
Algorithm formulation

\noindent
\textbf{Component-based algorithm.}
We introduce the algorithm \TAlg that we analyze in this section.
The algorithm partitions nodes into components, and
initially, each node is isolated (belongs to its own component).
For each pair of nodes $\set{x,y}$, \TAlg maintains a counter $C_{\set{x,y}}$ and increments it on every external request between $x$ and $y$.
Once $C_{\set{x,y}} = \alpha$, \TAlg merges the components of $u$ and $v$, and moves to the closest component respecting partitioning.
If no such partitioning exists, \TAlg resets all components to singleton components, resets all counters to $0$, and ends the phase.

@@

We describe the algorithm \RM for the online rematching problem as follows.
The input to \RM is a sequence of  requests
$\sigma:=\{\sigma_1,\dots, \sigma_m\}, \sigma_t:=\{x,y\} \in V^2, x \neq y$.
We maintain a counter $C_{\set{x,y}}$ for each pair of nodes $\set{x,y}$ and increment it on every remote request between $x$ and $y$.
Once $C_{\set{x,y}} = \lambda$,
reset the counter and collocate the pair arbitrarily in one of the two clusters where $x$ or $y$ resides.

@@

We charge both \OPT and \RM whenever \RM collocates a pair.%(i.e., on a collocation event).
\RM collocates a pair always with a swap,%(i.e., two simultaneous migrations),
which  costs $2\alpha$,
while \OPT may save some costs by collocating multiple pairs at once.
% before they inflict too much communication cost.
 Therefore it pays the price of only one migration per pair  (\mahmoud{see Figure \ref{fig:TBD}}).
Hence,
whenever \OPT collocates a pair,
we charge it only the cost of moving a single node to the cluster of the other,
i.e., $\alpha$ (in contrast to $2\alpha$ on \RM).

\textbf{The charging scheme.}
Consider two  pairs that share the same node, 
i.e.~\emph{intersecting pairs},
and the set of requests that causes the collocation of both pairs,
at some  times during  $[1,m]$.
%i.e.~the entire duration of the sequence.
Observe that \OPT must pay a non-zero cost
for these requests over the entire $\sigma$,
since it cannot have both pairs initially collocated.
However,
we can charge the whole cost to \OPT only the first time \RM collocates a pair,
and not at any consequent time when \RM collocates it a second time.
Otherwise,
 \OPT is possibly charged for the same cost repeatedly.
For this reason,
we charge \OPT a cost inflicted by a pair,
if and only if  \OPT incurs that cost after the latest separation of the pair by \RM.
%%

\begin{proof}[Proof of Theorem \ref{thm:k=2}]
	Assume on request $\sigma_{t}=\set{u,v}$, 
	i.e., at (time) $t$,
	\RM collocates the pair $\set{u,v}$.
	This means,
	the value of $C_{\set{u,v}}$ at $t$,
	denoted by $C^t_{\set{u,v}}$, 
	reaches $\lambda$ immediately before \RM resets the counter,
	i.e.,
	$ C^t_{\set{u,v}} = \lambda$.
	We denote the set of all requests to a pair $\set{x,y}$ that arrive
	during $[t_1,t_2]$ by $\sigma_{\set{x,y}}[t_1,t_2]$,
	and its overall cost to \OPT by
	$\mathit{OPT} (\sigma_{\{u,v\}}[t_1,t_2])$.
	We may use $\sigma_{\set{x,y}}$ whenever
	 the interval $[t_1,t_2]$ is clear from the context.
	%
	%Else, this is not the first time and
	%Alg collocates $\{u,v\}$ also some time prior to $t$.

>>>>

\noindent
\textbf{Component-based algorithm.}
The algorithm \TAlg partitions nodes into components, and
initially, each node is isolated (belongs to its own component).
For each pair of nodes $\set{x,y}$, \TAlg maintains a counter $C_{\set{x,y}}$ and increments it on every external request between $x$ and $y$.
Once $C_{\set{x,y}} = \alpha$, \TAlg merges the components of $u$ and $v$, and moves to the closest component respecting partitioning.
If no such partitioning exists, \TAlg resets all components to singleton components, resets all counters to $0$, and ends the phase.

@@

\noindent
\textbf{Algorithm ReMatch.} 
The algorithm ReMatch (\RM) maintains a counter $C_{\set{x,y}}$ for each pair of nodes $\set{x,y}$ and increments it on every remote request between $x$ and $y$.
Once $C_{\set{x,y}} = \lambda$,
it resets the counter $C_{\set{x,y}}:=0$ and collocates the pair by swapping $x$ with the node collocated with $y$.

\noindent
\textbf{The charging scheme.}
We charge both \OPT and \RM whenever \RM collocates a pair.%(i.e., on a collocation event).
\RM collocates a pair always with a swap,%(i.e., two simultaneous migrations),
which  costs $2\alpha$,
while \OPT may save some costs by collocating multiple pairs at once.
% before they inflict too much communication cost.
 Therefore it pays the price of only one migration per pair  (\mahmoud{see Figure \ref{fig:TBD}}).
Hence,
whenever \OPT collocates a pair,
we charge it only the cost of moving a single node to the cluster of the other,
i.e., $\alpha$ (in contrast to $2\alpha$ on \RM).

Consider two  pairs that share the same node, 
i.e.~\emph{intersecting pairs},
and the set of requests that causes the collocation of both pairs,
at some  times during  $[1,m]$.
%i.e.~the entire duration of the sequence.
Observe that \OPT must pay a non-zero cost
for these requests over the entire $\sigma$,
since it cannot have both pairs initially collocated.
However,
we can charge the whole cost to \OPT only the first time \RM collocates a pair,
and not at any consequent time when \RM collocates it a second time.
Otherwise,
 \OPT is possibly charged for the same cost repeatedly.
For this reason,
we charge \OPT a cost inflicted by a pair,
if and only if  \OPT incurs that cost after the latest separation of the pair by \RM.
%%

@@

\begin{proof}%[Proof of Theorem \ref{thm:k=2}]
	Fix an input sequence of requests
$\sigma:=\{\sigma_1,\dots, \sigma_m\}$.
	Assume on request $\sigma_{t}=\set{u,v}$, 
	i.e., at (time) $t$,
	\RM collocates the pair $\set{u,v}$.
	This means,
	the value of $C_{\set{u,v}}$ at $t$,
	denoted by $C^t_{\set{u,v}}$, 
	reaches $\lambda$ immediately before \RM resets the counter,
	i.e.,
	$ C^t_{\set{u,v}} = \lambda$.
	We denote the set of all requests to a pair $\set{x,y}$ that arrive
	during $[t_1,t_2]$ by $\sigma_{\set{x,y}}[t_1,t_2]$,
	and its overall cost to \OPT by
	$\mathit{OPT} (\sigma_{\{u,v\}}[t_1,t_2])$.
	We may use $\sigma_{\set{x,y}}$ whenever
	 the interval $[t_1,t_2]$ is clear from the context.
	%
	%Else, this is not the first time and
	%Alg collocates $\{u,v\}$ also some time prior to $t$.
